Evaluation of the repository

### 2024-10-25 pages/repo_evaluation.qmd
docs(repo evaluation): add johnson 2021

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
  'Huang et al. 2019 (3/8)': [3, 0, 9, 0],
  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
  'Kim et al. 2021 (10/10)': [5, 0, 7, 0],
  'Anagnostou et al. 2022 (1/1)': [10, 0, 2, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [3, 0, 9, 0],
  'Wood et al. 2021 (5/5)': [4, 0, 8, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

The remaining three studies were fully reproduced and met 33.3%, 41.7% and 83.3%.

@@

```{python}
plot_scatter('Unique badge criteria met',
             sho = 25,
             hua = 25,
             lim = 25,
             kim = 41.7,
             ana = 83.3,
             her = 25,
             woo = 33.3)
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badge_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
  'Huang et al. 2019 (3/8)': [0, 0, 12, 0],
  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
  'Kim et al. 2021 (10/10)': [3, 0, 9, 0],
  'Anagnostou et al. 2022 (1/1)': [5, 0, 7, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [0, 0, 12, 0],
  'Wood et al. 2021 (5/5)': [5, 0, 7, 0]
}
badge_wide = pd.DataFrame(badge_dict, index=col).T

@@

Not certain how meaningful these numbers are, as we have imbalanced numbers of different types of badge, and meeting certain popular criteria will quite weight what is met v.s. not.

Feel that looking at the criteria met is a bit more meaningful? And then specific examples of how that translates into badges - e.g. none meeting ACM "Artifacts Evaluated - Functional" as requires xyz and these are commonly not met.

```{python}
plot_scatter('Badges awarded',
             sho = 25,
             hua = 0,
             lim = 25,
             kim = 25,
             ana = 41.7,
             her = 0,
             woo = 41.7)
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
essential_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [2, 0, 6, 0],
  'Huang et al. 2019 (3/8)': [2, 0, 6, 0],
  'Lim et al. 2020 (9/9)': [2, 0, 6, 0],
  'Kim et al. 2021 (10/10)': [4, 1, 3, 0],
  'Anagnostou et al. 2022 (1/1)': [7, 0, 1, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [2, 0, 6, 0],
  'Wood et al. 2021 (5/5)': [2, 0, 6, 0]
}
essential_wide = pd.DataFrame(essential_dict, index=col).T

@@

Similar to journal criteria (unsurprisingly, as looking at similar things) - most studies meet very few and have range of reproduction success. Two met more, and both were reproduced.

@@

```{python}
plot_scatter('Essential STARS components met',
             sho = 25,
             hua = 25,
             lim = 25,
             kim = 50,
             ana = 87.5,
             her = 25,
             woo = 25)
```

@@

```{python}
# Create dataframe of results
optional_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [0, 0, 5, 0],
  'Huang et al. 2019 (3/8)': [2, 0, 3, 0],
  'Lim et al. 2020 (9/9)': [0, 0, 5, 0],
  'Kim et al. 2021 (10/10)': [0, 0, 5, 0],
  'Anagnostou et al. 2022 (1/1)': [1, 1, 3, 0],
  'Johnson et al. 2021 (X/X)': [0, 0, 0, 1],
  'Hernandez et al. 2015 (1/8)': [0, 0, 5, 0],
  'Wood et al. 2021 (5/5)': [0, 0, 5, 0]
}
optional_wide = pd.DataFrame(optional_dict, index=col).T

@@

```{python}
plot_scatter('Optional STARS components met',
             sho = 0,
             hua = 40,
             lim = 0,
             kim = 0,
             ana = 20,
             her = 0,
             woo = 0)
```

@@

| Item | S | Hu | L | K | A | J | He | W |
| - | - | - | - | - | - | - | - | - | - |
| **Criteria related to how artefacts are shared** |
| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | ❌ | ❌ |
| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
| Includes an open license | ❌ | ✅ | ❌ | ✅ | ✅ |<!--TODO--> | ❌ | ❌ |
| **Criteria related to what artefacts are shared** |
| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
| **Criteria related to the structure and documentation of the artefacts** |
| Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ |<!--TODO--> | ✅ | ❌ |
| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
| Artefacts are carefully documented (more than sufficient - i.e. to the extent that reuse and repurposing is facilitated - e.g. changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
| **Criteria related to running and reproducing results** |
| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ |<!--TODO--> | ✅ | ✅ |
| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
| Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Archive': [1, 0, 6, 0],
  'ID': [1, 0, 6, 0],
  'License': [3, 0, 4, 0],
  'Relevant': [7, 0, 0, 0],
  'Complete': [1, 0, 6, 0],
  'Structured for reuse': [3, 0, 4, 0],
  'Sufficient docs': [1, 0, 6, 0],
  'Careful docs': [1, 0, 6, 0],
  'Step-by-step README': [1, 0, 6, 0],
  'Execute': [7, 0, 0, 0],
  'Reproduced': [5, 0, 2, 0],
  'One hour': [0, 0, 7, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

**Includes an open license**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open license to their work, to enable us to use it. Gladly, all authors we contacted kindly add these on request. However, it's worth noting that this was a relatively common issue, and one of the most important, since it completely prevents reuse if excluded.

@@

**Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)**: In cases where this was not met, this was often related to hard-coding of parameters, or set up of code in a way that - alike hard-coding - made it much harder to reuse the model (in this context, to reuse them between different scenarios).

**Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions)**: Only two studies had any form of documentation - these were READMEs for @kim_modelling_2021 and @anagnostou_facs-charm_2022 - but this criteria also required "package versions" which were uncommon. However, focusing on the READMEs, in both these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is.

@@

**Scripts can be successfully executed**: This is true, though I did allow troubleshooting, which sometimes took a while. Hence, the importance of e.g. environments and scripts being provided in a runnable format (both covered on the [reflections page](reflections.qmd)), since these are the hurdles to successfully executing scripts.

@@

| Item | S | Hu | L | K | A | J | He | W |
| - | - | - | - | - | - | - | - | - | - |
| **“Open objects” badges** |
| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ |<!--TODO--> | ❌ | ❌ |
| **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open license<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
| **"Object review" badges** |
| **ACM "Artifacts Evaluated - Functional"**<br>• Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
| **ACM "Artifacts Evaluated - Reusable"**<br>• Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are carefully documented (more than sufficient - i.e. to the extent that reuse and repurposing is facilitated - e.g. changing parameters, reusing for own purpose)<br>• Artefacts are relevant to and contribute to the article's results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed<br>• Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ✅ |
| **"Reproduced" badges** |
| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ |<!--TODO--> | ❌ | ✅ |
| **Psychological Science "Computational Reproducibility"**<br>• Independent party regenerated results using the authors research artefacts<br>• Reproduced within approximately one hour (excluding compute time)<br>• Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ |<!--TODO--> | ❌ | ❌ |
: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badges_dict = {
  'NISO “Open Research<br>Objects (ORO)”': [1, 0, 6, 0],
  'NISO “Open Research<br>Objects - All (ORO-A)”': [0, 0, 7, 0],
  'ACM “Artifacts<br>Available”': [1, 0, 6, 0],
  'COS “Open Code”': [0, 0, 7, 0],
  'IEEE “Code Available”': [1, 0, 6, 0],
  'ACM “Artifacts<br>Evaluated - Functional”': [0, 0, 7, 0],
  'ACM “Artifacts<br>Evaluated - Reusable”': [0, 0, 7, 0],
  'IEEE “Code Reviewed”': [1, 0, 6, 0],
  'NISO “Results<br>Reproduced (ROR-R)”': [5, 0, 2, 0],
  'ACM “Results Reproduced”': [5, 0, 2, 0],
  'IEEE “Code Reproducible”': [5, 0, 2, 0],
  'Psychological Science<br>“Computational Reproducibility”': [0, 0, 7, 0],
}
badges_wide = pd.DataFrame(badges_dict, index=col).T

@@

A **complete set of materials** was required by *IEEE “Code Available”* and *IEEE “Code Reviewed”* - but this was only met by one study, as studies commonly did not include code for scenarios or creation of figures and tables. It was also required by *ACM “Artifacts Evaluated - Functional and Reusable”* badges, but since that one study didn't meet their **documentation** requirements, none were awarded these badges.

@@

Besides the reproduction and documentation criteria, the final badge *Psychological Science “Computational Reproducibility”* was somewhat impossible to award since it required **reproduction within an hour**, which was somewhat impossible in our procedures, since we read the article and set-up etc beforehand.

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stars_dict = {
  'Open license': [3, 0, 4, 0],
  'Dependency management': [1, 1, 5, 0],
  'FOSS model': [8, 0, 0, 0],
  'Minimum documentation': [2, 0, 5, 0],
  'ORCID': [0, 0, 7, 0],
  'Citation information': [1, 0, 6, 0],
  'Remote code repository': [7, 0, 0, 0],
  'Open science archive': [1, 0, 6, 0],
  'Enhanced documentation': [0, 0, 7, 0],
  'Documentation hosting': [0, 0, 7, 0],
  'Online coding environment': [0, 0, 7, 0],
  'Model interface': [2, 0, 5, 0],
  'Web app hosting': [1, 1, 5, 0],
}
stars_wide = pd.DataFrame(stars_dict, index=col).T

@@

As in badge criteria reflections: **open license**, **minimum documentation**, and **open science archive**. <!--TODO: Consider re minimum documentation: Kim met for STARS but not for badges. Double-check that decision-->

@@

**Enhanced documentation**: Only two studies had any documentation, and neither met these extensive requirements. I anticipate - if any had met this - it would've made the reproduction very quick and easy!

@@

* @shoaib_simulation_2021 - 30m
* @huang_optimizing_2019 - 17m
* @lim_staff_2020 - 18m
* @kim_modelling_2021 - 18m
* @anagnostou_facs-charm_2022 - 19m
* @johnson_cost_2021 - <!--TODO-->
* @hernandez_optimal_2015 - 13m
* @wood_value_2021 - 14m

>>>>

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
  'Huang et al. 2019 (3/8)': [3, 0, 9, 0],
  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
  'Kim et al. 2021 (10/10)': [5, 0, 7, 0],
  'Anagnostou et al. 2022 (1/1)': [10, 0, 2, 0],
  'Johnson et al. 2021 (4/5)': [4, 0, 8, 0],
  'Hernandez et al. 2015 (1/8)': [3, 0, 9, 0],
  'Wood et al. 2021 (5/5)': [4, 0, 8, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

Two studies met 33% of criteria, and these were 80% and 100% reproduced.

The remaining two studies were fully reproduced and met 41.7% and 83.3% of criteria.

@@

```{python}
plot_scatter('Unique badge criteria met',
             sho = 25,
             hua = 25,
             lim = 25,
             kim = 41.7,
             ana = 83.3,
             joh = 33.3,
             her = 25,
             woo = 33.3)
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badge_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [3, 0, 9, 0],
  'Huang et al. 2019 (3/8)': [0, 0, 12, 0],
  'Lim et al. 2020 (9/9)': [3, 0, 9, 0],
  'Kim et al. 2021 (10/10)': [3, 0, 9, 0],
  'Anagnostou et al. 2022 (1/1)': [5, 0, 7, 0],
  'Johnson et al. 2021 (4/5)': [3, 0, 9, 0],
  'Hernandez et al. 2015 (1/8)': [0, 0, 12, 0],
  'Wood et al. 2021 (5/5)': [5, 0, 7, 0]
}
badge_wide = pd.DataFrame(badge_dict, index=col).T

@@

Not certain how meaningful these numbers are, as we have imbalanced numbers of different types of badge, and meeting certain popular criteria will weight what is met v.s. not.

Feel that looking at the criteria met is a bit more meaningful? And then specific examples of how that translates into badges - e.g.

* None meeting ACM "Artifacts Evaluated - Functional" as requires xyz and these are commonly not met.
* For several, they meet three badges, but those three badges have one criteria: reproducing results.

Also, it's important to remember here that the criteria used for these were based on what could be found about each badge online, but we likely differences in our procedure (e.g. allowed troubleshooting for execution and reproduction, not under tight time pressure to complete). Moreover, we focus only on reproduction of the discrete-event simulation, and not on other aspects of the article. We cannot guarantee that the badges below would have been awarded in practice by these journals (and, in fact, know likely not for many).

```{python}
plot_scatter('Badges awarded',
             sho = 25,
             hua = 0,
             lim = 25,
             kim = 25,
             ana = 41.7,
             joh = 25,
             her = 0,
             woo = 41.7)
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
essential_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [2, 0, 6, 0],
  'Huang et al. 2019 (3/8)': [2, 0, 6, 0],
  'Lim et al. 2020 (9/9)': [2, 0, 6, 0],
  'Kim et al. 2021 (10/10)': [4, 1, 3, 0],
  'Anagnostou et al. 2022 (1/1)': [7, 0, 1, 0],
  'Johnson et al. 2021 (4/5)': [4, 2, 2, 0],
  'Hernandez et al. 2015 (1/8)': [2, 0, 6, 0],
  'Wood et al. 2021 (5/5)': [2, 0, 6, 0]
}
essential_wide = pd.DataFrame(essential_dict, index=col).T

@@

Similar to journal criteria (unsurprisingly, as looking at similar things) - most studies meet very few and have wide range of reproduction success, from 12.5% to 100%. Three met more, and these were 80% to 100% reproduced.

@@

```{python}
plot_scatter('Essential STARS components met',
             sho = 25,
             hua = 25,
             lim = 25,
             kim = 50,
             ana = 87.5,
             joh = 50,
             her = 25,
             woo = 25)
```

@@

```{python}
# Create dataframe of results
optional_dict = {
  'Shoaib and Ramamohan<br>2021 (16/17)': [0, 0, 5, 0],
  'Huang et al. 2019 (3/8)': [2, 0, 3, 0],
  'Lim et al. 2020 (9/9)': [0, 0, 5, 0],
  'Kim et al. 2021 (10/10)': [0, 0, 5, 0],
  'Anagnostou et al. 2022 (1/1)': [1, 1, 3, 0],
  'Johnson et al. 2021 (4/5)': [0, 0, 5, 0],
  'Hernandez et al. 2015 (1/8)': [0, 0, 5, 0],
  'Wood et al. 2021 (5/5)': [0, 0, 5, 0]
}
optional_wide = pd.DataFrame(optional_dict, index=col).T

@@

```{python}
plot_scatter('Optional STARS components met',
             sho = 0,
             hua = 40,
             lim = 0,
             kim = 0,
             ana = 20,
             joh = 0,
             her = 0,
             woo = 0)
```

@@

| Item | S | Hu | L | K | A | J | He | W |
| - | - | - | - | - | - | - | - | - | - |
| **Criteria related to how artefacts are shared** |
| Stored in a permanent archive that is publicly and openly accessible | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| Includes an open licence | ❌ | ✅ | ❌ | ✅ | ✅ | ✅ | ❌ | ❌ |
| **Criteria related to what artefacts are shared** |
| Artefacts are relevant to and contribute to the article’s results | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
| Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
| **Criteria related to the structure and documentation of the artefacts** |
| Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ✅ | ✅ | ❌ | ✅ | ❌ |
| Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| Artefacts are carefully documented (more than sufficient - i.e. to the extent that reuse and repurposing is facilitated - e.g. changing parameters, reusing for own purpose) | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| **Criteria related to running and reproducing results** |
| Scripts can be successfully executed | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |
| Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
| Reproduced within approximately one hour (excluding compute time) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'Archive': [1, 0, 7, 0],
  'ID': [1, 0, 7, 0],
  'Licence': [4, 0, 4, 0],
  'Relevant': [8, 0, 0, 0],
  'Complete': [1, 0, 7, 0],
  'Structured for reuse': [3, 0, 5, 0],
  'Sufficient docs': [1, 0, 7, 0],
  'Careful docs': [1, 0, 7, 0],
  'Step-by-step README': [1, 0, 7, 0],
  'Execute': [8, 0, 0, 0],
  'Reproduced': [6, 0, 2, 0],
  'One hour': [0, 0, 8, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

**Includes an open licence**: This had a big impact on our ability to complete reproductions, as we had to ask authors to add an open licence to their work, to enable us to use it. Gladly, all authors we contacted kindly add these on request. However, it's worth noting that this was a relatively common issue, and one of the most important, since it completely prevents reuse if excluded.

@@

**Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)**: In cases where this was not met, this was often related to hard-coding of parameters, or set up of code in a way that - alike hard-coding - made it much harder to reuse the model (in this context, to reuse them between different scenarios) - or quite a busy/cluttered repository which was confusing to navigate.

**Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions)**: Only three studies had any documentation - READMEs for @kim_modelling_2021, @anagnostou_facs-charm_2022 and @johnson_cost_2021 - but this criteria also required "package versions" which were uncommon. However, focusing on the READMEs, in each of these cases it was great to have these, guiding on how to run the scripts, or on what each folder/file in the repository is.

@@

**Scripts can be successfully executed**: This is true, though I did allow troubleshooting, which sometimes took a long while. Hence, the importance of e.g. environments and scripts being provided in a runnable format (both covered on the [reflections page](reflections.qmd)), since these are the hurdles to successfully executing scripts.

@@

| Item | S | Hu | L | K | A | J | He | W |
| - | - | - | - | - | - | - | - | - | - |
| **“Open objects” badges** |
| **NISO "Open Research Objects (ORO)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| **NISO "Open Research Objects - All (ORO-A)"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
| **ACM "Artifacts Available"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier | ❌ | ❌ | ❌ | ❌ | ✅ | ❌ | ❌ | ❌ |
| **COS "Open Code"**<br>• Stored in a permanent archive that is publicly and openly accessible<br>• Has a persistent identifier<br>• Includes an open licence<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
| **IEEE "Code Available"**<br>• Complete set of materials shared (as would be needed to fully reproduce article) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
| **"Object review" badges** |
| **ACM "Artifacts Evaluated - Functional"**<br>• Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are relevant to and contribute to the article’s results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
| **ACM "Artifacts Evaluated - Reusable"**<br>• Artefacts are sufficiently documented (i.e. to understand how it works, to enable it to be run, including package versions)<br>• Artefacts are carefully documented (more than sufficient - i.e. to the extent that reuse and repurposing is facilitated - e.g. changing parameters, reusing for own purpose)<br>• Artefacts are relevant to and contribute to the article's results<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed<br>• Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community) | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
| **IEEE "Code Reviewed"**<br>• Complete set of materials shared (as would be needed to fully reproduce article)<br>• Scripts can be successfully executed | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ✅ |
| **"Reproduced" badges** |
| **NISO "Results Reproduced (ROR-R)"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
| **ACM "Results Reproduced"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
| **IEEE "Code Reproducible"**<br>• Independent party regenerated results using the authors research artefacts | ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
| **Psychological Science "Computational Reproducibility"**<br>• Independent party regenerated results using the authors research artefacts<br>• Reproduced within approximately one hour (excluding compute time)<br>• Artefacts are well structured/organised (e.g. to the extent that reuse and repurposing is facilitated, adhering to norms and standards of research community)<br>• Artefacts are clearly documented and accompanied by a README file with step-by-step instructions on how to reproduce results in the manuscript | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |
: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badges_dict = {
  'NISO “Open Research<br>Objects (ORO)”': [1, 0, 7, 0],
  'NISO “Open Research<br>Objects - All (ORO-A)”': [0, 0, 8, 0],
  'ACM “Artifacts<br>Available”': [1, 0, 7, 0],
  'COS “Open Code”': [0, 0, 8, 0],
  'IEEE “Code Available”': [1, 0, 7, 0],
  'ACM “Artifacts<br>Evaluated - Functional”': [0, 0, 8, 0],
  'ACM “Artifacts<br>Evaluated - Reusable”': [0, 0, 8, 0],
  'IEEE “Code Reviewed”': [1, 0, 7, 0],
  'NISO “Results<br>Reproduced (ROR-R)”': [6, 0, 2, 0],
  'ACM “Results Reproduced”': [6, 0, 2, 0],
  'IEEE “Code Reproducible”': [6, 0, 2, 0],
  'Psychological Science<br>“Computational Reproducibility”': [0, 0, 8, 0],
}
badges_wide = pd.DataFrame(badges_dict, index=col).T

@@

A **complete set of materials** was required by *IEEE “Code Available”* and *IEEE “Code Reviewed”* - but this was only met by one study, as studies commonly did not include code for scenarios or creation of figures and tables. It was also required by *ACM “Artifacts Evaluated - Functional and Reusable”* badges, but since that one study didn't meet their **documentation** requirements, none were awarded those badges.

@@

The final badge *Psychological Science “Computational Reproducibility”* had several criteria, but of importance, one of those was to complete the **reproduction within an hour**. This was somewhat impossible in our procedures, since we read the article and set-up etc beforehand, and so none were awarded this badge.

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stars_dict = {
  'Open licence': [4, 0, 4, 0],
  'Dependency management': [1, 2, 5, 0],
  'FOSS model': [8, 0, 0, 0],
  'Minimum documentation': [2, 1, 5, 0],
  'ORCID': [0, 0, 8, 0],
  'Citation information': [2, 0, 6, 0],
  'Remote code repository': [8, 0, 0, 0],
  'Open science archive': [1, 0, 7, 0],
  'Enhanced documentation': [0, 0, 8, 0],
  'Documentation hosting': [0, 0, 8, 0],
  'Online coding environment': [0, 0, 8, 0],
  'Model interface': [2, 0, 6, 0],
  'Web app hosting': [1, 1, 6, 0],
}
stars_wide = pd.DataFrame(stars_dict, index=col).T

@@

These topics were covered in the badge criteria reflections: **open licence**, **minimum documentation**, and **open science archive**. <!--TODO: Consider re minimum documentation: Kim met for STARS but not for badges. Double-check that decision-->

@@

**Enhanced documentation**: Only three studies had any documentation, and neither met these extensive requirements. I anticipate - if any had met this - it would've made the reproduction very quick and easy!

@@

* @shoaib_simulation_2021 - 30m
* @huang_optimizing_2019 - 17m
* @lim_staff_2020 - 18m
* @kim_modelling_2021 - 18m
* @anagnostou_facs-charm_2022 - 19m
* @johnson_cost_2021 - 20m
* @hernandez_optimal_2015 - 13m
* @wood_value_2021 - 14m
